## STAT 540 Seminar 04: Two group comparisons and data aggregation
### Hao Chen
__2014-02-10__

* <dim id="1a">[Load the photoRec dataset and required packages](#1b)
* <dim id="2a">[The "you try" question](#2b)
* <dim id="3a">[Take-home problem](#3b)

> The R markdown file can be found on my [Github](https://github.com/nelsonch/stat540-2014-chen-hao/blob/master/seminar%2004/seminar04.Rmd).

```{r include = FALSE}
opts_chunk$set(tidy = F, warning=F, comment=NA, prompt=T)
```

```{r echo = FALSE}
htmlPrint <- function(x, ..., digits = 0, include.rownames = FALSE) {
  print(xtable(x, digits = digits, ...), type = 'html', 
        include.rownames = include.rownames)
  }
```

### <dim id="1b">[Load the photoRec dataset and required packages](#1a)
The following datasets will be covered in this seminar:
* [GSE4051_data.tsv](https://github.com/jennybc/stat540_2014/blob/master/examples/photoRec/data/GSE4051_data.tsv): full data matrix 
* [GSE4051_design.rds](https://github.com/jennybc/stat540_2014/blob/master/examples/photoRec/data/GSE4051_design.rds): experimental design

Load required datasets:
```{r}
prDat <- read.table("GSE4051_data.tsv")
str(prDat, max.level = 0)
```

```{r}
prDes <- readRDS("GSE4051_design.rds")
str(prDes)
```

Load required R packages:
```{r}
library(lattice)   # for plotting
library(plyr)  # for data aggregation
library(xtable) # for table display
library(limma)  # for venn diagram
```

### <dim id="2b">[The "you try" question](#2a)
[You try](http://ugrad.stat.ubc.ca/~stat540/seminars/seminar04_compileNotebook-dataAggregation-twoGroupComparison.html#two-sample-tests----one-gene): Draw a different gene at random. Use the t test, with and without the common variance assumption, the Wilcoxon, and/or the Kolmogorov-Smirnov test to assess differential expression. Pull test statistics and/or p-values from the different approaches into an common object, like a readable table. Hint: wilcox.test(), ks.test().

```{r}
set.seed(540)
(theGene <- sample(1:nrow(prDat), 1))
pDat <- data.frame(prDes, gExp = unlist(prDat[theGene, ]))
```

Make a stripplot to sanity test the t test result.
```{r}
stripplot(gType ~ gExp, pDat)
```

```{r results = 'asis'}
ttRes <- t.test(gExp ~ gType, pDat)
wtRes <- wilcox.test(gExp ~ gType, pDat)
ksRes <- with(pDat, ks.test(gExp[gType == "NrlKO"], gExp[gType == "wt"]))
Res <- data.frame(method = c("t.test", "wilcox.test", "ks.test"),
                  test.stat = c(ttRes$stat, wtRes$stat, ksRes$stat),
                  p.value = c(ttRes$p.val, wtRes$p.val, ksRes$p.val))
htmlPrint(Res, digits = 3)
```

### <dim id="3b">[Take-home problem](#3a) ([link here](http://ugrad.stat.ubc.ca/~stat540/seminars/seminar04_compileNotebook-dataAggregation-twoGroupComparison.html#ideas-for-take-home-work))

#### Step 1: Make a numeric matrix with p-values for 100 randomly picked genes for various two-group tests (t.test, wilcox.test and ks.test).

Randomly draw 100 genes and aggregate the data.
```{r}
set.seed(540)
theGenes <- sample(1:nrow(prDat), 100)
keepGenes <- rownames(prDat)[theGenes]
miniDat <- subset(prDat, rownames(prDat) %in% keepGenes)
miniDat <- data.frame(gExp = as.vector(t(as.matrix(miniDat))),
                      gene = factor(rep(rownames(miniDat), each = ncol(miniDat)),
                                    levels = keepGenes))
miniDat <- suppressWarnings(data.frame(prDes, miniDat))
str(miniDat)
```

The p-values for various two-group tests. The results are sorted by _t_ test.
```{r results = 'asis'}
Res <- ddply(miniDat, ~ gene, function(x){
  ttRes <- t.test(gExp ~ gType, x)
  wtRes <- wilcox.test(gExp ~ gType, x)
  ksRes <- with(x, ks.test(gExp[gType == "NrlKO"], gExp[gType == "wt"]))
  round(c(t.test = ttRes$p.val, wilcox.test = wtRes$p.val, ks.test = ksRes$p.val), 3)               
})
Res <- arrange(Res, t.test)
htmlPrint(Res, digits = 3)
```

The following figures show the first 3 clear 'hits' and last 3 clear boring genes from the randomly sampled 100 genes, according to the p-value from _t_ test.
```{r fig.width=8, fig.height=5}
hitGene <- Res$gene[1:3]
hitDat <- subset(miniDat, gene %in% hitGene)
borGene <- Res$gene[98:100]
borDat <- subset(miniDat, gene %in% borGene)
stripplot(gType ~ gExp | gene, hitDat, group = gType, auto.key = TRUE,
          scales = list(x = list(relation = "free")), layout = c(3, 1), 
          main = "The first 3 hits among 100 randomly picked genes")
stripplot(gType ~ gExp | gene, borDat, group = gType, auto.key = TRUE,
          scales = list(x = list(relation = "free")), layout = c(3, 1),
          main = "The last 3 boring genes among 100 randomly picked genes")
```

#### Step 2: Scatterplot different kinds of p-values against each other.
```{r}
pairDat <- Res[, c("t.test", "wilcox.test", "ks.test")]
panel.cor <- function(x, y, digits=2, cex.cor)
{
  usr <- par("usr"); on.exit(par(usr))
  par(usr = c(0, 1, 0, 1))
  r <- abs(cor(x, y))
  txt <- format(c(r, 0.123456789), digits=digits)[1]
  text(0.5, 0.5, paste("r=",txt), cex=1.5)
}
pairs(pairDat, upper.panel=panel.cor)
```

#### Step 3: Convert your numeric matrix of p-values into a matrix of TRUE/FALSE or zeros and ones by hard-threshholding, e.g. conventional 0.05 level, and make some interesting row or column summaries.

Convert the above matrix of p-values into a matrix of 1/0 (1 stands for significance), the cut-off p-value is 0.05. The following table shows the first 10 rows of such a table. 
```{r results = 'asis'}
cutoff <- 0.05
sumRes <- Res[, c("t.test", "wilcox.test", "ks.test")]
sumRes <- matrix(as.numeric(sumRes < cutoff), nrow = nrow(sumRes))
colnames(sumRes) <- c("t.test", "wilcox.test", "ks.test")
tfRes <- data.frame(gene = Res$gene, as.data.frame(sumRes))
htmlPrint(tfRes[1:10, ])
```

How many genes are significant according to the different tests? 
```{r}
vennDiagram(vennCounts(sumRes[, c("t.test", "wilcox.test", "ks.test")]))
```

Show the 18 genes which are significant from at least one of the tests. 
```{r results = 'asis'}
testsum <- rowSums(sumRes)
sumRes <- as.data.frame(sumRes)
sumRes <- cbind(gene = Res$gene, sumRes, sum.test = testsum)
hitRes <- arrange(subset(sumRes, sum.test > 0), desc(sum.test))
htmlPrint(hitRes)
```

The following figure shows the stripplot of the 18 'hits' among 100 randomly picekd genes. 

```{r fig.width=12, fig.height=8}
hitGene <- hitRes$gene
hitDat <- subset(miniDat, gene %in% hitGene)
stripplot(gType ~ gExp | gene, hitDat, group = gType, auto.key = TRUE,
          scales = list(x = list(relation = "free")), layout = c(6, 3), 
          main = "The 18 'hits' among 100 randomly picked genes")
```
